---
title: "PML01"
author: "GgYy"
date: "20160710"
output: html_document
---
1.Install needed packages
```{r}
#install.packages("data.table")
#install.packages("caret")
#install.packages("randomForest")
#install.packages("foreach")
#install.packages("rpart")
#install.packages("rpart.plot")
#install.packages("corrplot")
```



2.Load needed packages
```{r}
library(data.table)
library(caret)
library(randomForest)
library(foreach)
library(rpart)
library(rpart)
library(rpart.plot)
library(corrplot)
```



3.Read datas
```{r}
training_data <- read.csv("pml-training.csv", na.strings=c("#DIV/0!"," ", "", "NA", "NAs", "NULL"))
testing_data <- read.csv("pml-testing.csv", na.strings=c("#DIV/0!"," ", "", "NA", "NAs", "NULL"))
```



4.Clean datas
  Drop NAs, Drop highly corelated variables, drop variables whose contents are the same.
```{r}
#4.1 Drop columns with NAs
str(training_data)
cleantraining <- training_data[, -which(names(training_data) %in% c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window"))]
cleantraining = cleantraining[, colSums(is.na(cleantraining)) == 0] 
#4.2 Drop variables with same content
zerovariance =nearZeroVar(cleantraining[sapply(cleantraining, is.numeric)], saveMetrics=TRUE)
cleantraining = cleantraining[, zerovariance[, 'nzv'] == 0] 
#4.3.1 Return the correlation matrix in matrix format
correlationmatrix <- cor(na.omit(cleantraining[sapply(cleantraining, is.numeric)]))
dim(correlationmatrix)
correlationmatrixdegreesoffreedom <- expand.grid(row = 1:52, col = 1:52)
correlationmatrixdegreesoffreedom$correlation <- as.vector(correlationmatrix) 
#4.3.2 Remove highly correlated variables(up to 0.7)
removehighcorrelation <- findCorrelation(correlationmatrix, cutoff = .7, verbose = TRUE)
cleantraining <- cleantraining[, -removehighcorrelation] 
#4.4 Generally drop blanks
for(i in c(8:ncol(cleantraining)-1)) {cleantraining[,i] = as.numeric(as.character(cleantraining[,i]))}

for(i in c(8:ncol(testing_data)-1)) {testing_data[,i] = as.numeric(as.character(testing_data[,i]))} 
#4.5 Redefine to be used data
featureset <- colnames(cleantraining[colSums(is.na(cleantraining)) == 0])[-(1:7)]
modeldata <- cleantraining[featureset]
featureset 
```



5.Build model
  Split 60% for training and 40% for testing.
```{r}
idx <- createDataPartition(modeldata$classe, p=0.6, list=FALSE )
training <- modeldata[idx,]
testing <- modeldata[-idx,]
```
  5 fold cross validation is used.
```{r}

control <- trainControl(method="cv", 5)
modelRF<- train(classe ~ ., data=training, method="rf", trControl=control)
modelLDA<-train(classe ~ ., data=training, method="lda", trControl=control)
modelGBM<-train(classe ~ ., data=training, method="gbm", trControl=control)
modelRpart<-train(classe ~ ., data=training, method="rpart", trControl=control)
```
  Review the perfomrance of the model
```{r}
predictRF<-predict(modelRF,testing)
predictLDA<-predict(modelLDA,testing)
predictGBM<-predict(modelGBM,testing)
predictRpart<-predict(modelRpart,testing)

confusionMatrix(testing$classe,predictRF)
confusionMatrix(testing$classe,predictLDA)
confusionMatrix(testing$classe,predictGBM)
confusionMatrix(testing$classe,predictRpart)

accuracyRF<-postResample(predictRF,testing$classe)
accuracyLDA<-postResample(predictLDA,testing$classe)
accuracyGBM<-postResample(predictGBM,testing$classe)
accuracyRpart<-postResample(predictRpart,testing$classe)

accuracyRF
accuracyLDA
accuracyGBM
accuracyRpart
```
  It shows that the highest accuracy of random forest model is 97.50%.

6.Predict
  Predict by using testing data
```{R, echo=TRUE}
model <- train(classe ~ ., data=training, method="rf", trControl=control, ntree=250)
result <- predict(model, training[, -length(names(training))])
result
#Considering the length, this part will not be shown
```


7.Answer the asked question
```{R}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

testing_data <- testing_data[featureset[featureset!='classe']]
answers <- predict(model, newdata=testing_data)
answers

pml_write_files(answers)
```
